Figures main manuscript

### 2019-07-16 code/figures.rmd
Removed visual confidence bands from Figure 3

```{r corr_per_effect_type-plot, cache = FALSE}
#tau2plot----
tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#I2plot----
I2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = s_I2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_x_continuous(name = "Effect size") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#H2plot----
H2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

>>>>

```{r corr_per_effect_type-plot, cache = FALSE}
#tau2plot----
tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#I2plot----
I2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = s_I2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_x_continuous(name = "Effect size") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#H2plot----
H2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different
